Insurance choice, decision assistance, and insurer steering

### 2021-05-03 finals/creed/creed-202105.Rmd
update slides
creed slides

.pull-left[
Exchanges relatively large, but...

- Large number of people still uninsured

- Many eligible for some type of subsidy on exchanges
]

.pull-right[
  ![:scale 150%](../pics/kff-uninsured.png)
]

@@

---
# Analysis of dominated choices

@@

---
# Analysis of switching

@@

# Effect of decision assistance

>>>>

.center[
  ![:scale 200%](../pics/kff-uninsured.png)
]

@@

---
# Estimation and identification

- Linear probability model of dominated choices or switching
- Dummy variable for receiving any assistance
- Selection on observables assumption (for now)

---
# Decision assistance and dominated choices

@@

---
# Decision assistance and switching

@@

# Effect of decision assistance on plan choice
